---
title: "Investigating Regionality of Porter School Motifs"
author: "Grace Acton"
date: "`r Sys.Date()`"
output: html_document
---

```{r load, echo=FALSE, warning=F}
library(tidyverse)
library(leaflet)
library(sf)
library(fontawesome)

motifs <- read_csv("data/rp_art_motifs_CLEAN.csv")

jdp <- motifs %>% 
  filter(grepl("Jonathan D. Poor", creator) & attribution == "signed")

rp <- motifs %>% 
  filter(grepl("Rufus Porter", creator) & attribution == "signed")
```

```{r initialize-leaflets, echo=FALSE}
jdp_map <- leaflet() %>% 
  addProviderTiles("Stamen.TonerLite") %>% 
  addCircleMarkers(
    data = jdp,
    radius = 30,
    opacity = 0.2,
    color = "green",
    fillColor = 'green'
  )

rp_map <- leaflet() %>% 
  addProviderTiles("Stamen.TonerLite") %>% 
  addCircleMarkers(
    data = rp,
    radius = 30,
    opacity = 0.2,
    color = "blue",
    fillColor = "blue"
  )
```

## Stenciled Village

```{r village}
filtered_data <- motifs %>% 
  filter(`village-stenciled` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Taupe Barn

```{r barn}
filtered_data <- motifs %>% 
  filter(`taupe-barn` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Steamboat

```{r steamboat}
filtered_data <- motifs %>% 
  filter(`steamboat` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Tree shaped like a Hat

```{r}
filtered_data <- motifs %>% 
  filter(`hat-tree` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Birds

```{r}
filtered_data <- motifs %>% 
  filter(`birds` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Fallen tree in the branches of another tree

```{r}
filtered_data <- motifs %>% 
  filter(`fallen-tree` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Paired Trees

```{r}
filtered_data <- motifs %>% 
  filter(`pair-tree` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Horses

```{r}
filtered_data <- motifs %>% 
  filter(`horses` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Dogs

```{r}
filtered_data <- motifs %>% 
  filter(`dogs` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Deer

```{r}
filtered_data <- motifs %>% 
  filter(`deer` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Militiamen

```{r}
filtered_data <- motifs %>% 
  filter(`militia` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Farm

```{r}
filtered_data <- motifs %>% 
  filter(`farm` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Stenciled Ferns

```{r}
filtered_data <- motifs %>% 
  filter(`ferns` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## White Federal-style House

```{r}
filtered_data <- motifs %>% 
  filter(`white-house` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Cluster of 3 Buildings

```{r}
filtered_data <- motifs %>% 
  filter(`three-buildings` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Tree with the Center Chopped Out

```{r}
filtered_data <- motifs %>% 
  filter(`nocenter-tree` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Faux Chair Rail

```{r}
filtered_data <- motifs %>% 
  filter(`chair-rail` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Fences

```{r}
filtered_data <- motifs %>% 
  filter(`fence` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Man in a Sailing Skiff

```{r}
filtered_data <- motifs %>% 
  filter(`skiff` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Hand-painted Village

```{r}
filtered_data <- motifs %>% 
  filter(`village-handpaint` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Cows

```{r}
filtered_data <- motifs %>% 
  filter(`cows` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Windmill

```{r}
filtered_data <- motifs %>% 
  filter(`windmill` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Observatory

```{r}
filtered_data <- motifs %>% 
  filter(`observatory` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Dense Woods

```{r}
filtered_data <- motifs %>% 
  filter(`woods` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Octagonal Building

```{r}
filtered_data <- motifs %>% 
  filter(`octagon` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Waterfall

```{r}
filtered_data <- motifs %>% 
  filter(`waterfall` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Stenciled Border

```{r}
filtered_data <- motifs %>% 
  filter(`border-stenciled` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Man with a Gun

```{r}
filtered_data <- motifs %>% 
  filter(`man-shooting` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Large Red House

```{r}
filtered_data <- motifs %>% 
  filter(`red-house` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Orchard

```{r}
filtered_data <- motifs %>% 
  filter(`orchard` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Red Sumac

```{r}
filtered_data <- motifs %>% 
  filter(`sumac` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Signpost

```{r}
filtered_data <- motifs %>% 
  filter(`signpost` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Galleon

```{r}
filtered_data <- motifs %>% 
  filter(`galleon` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Mountains

```{r}
filtered_data <- motifs %>% 
  filter(`moountains` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Half Tree at the Side of Mural

```{r}
filtered_data <- motifs %>% 
  filter(`half-tree` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Sailing Vessels

```{r}
filtered_data <- motifs %>% 
  filter(`sailboats` == TRUE)

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

# Motifs with clear spatial patterns

## Steamboat

```{r steamboat-overlay}
filtered_data <- motifs %>% 
  filter(`steamboat` == TRUE)

rp_map %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```

## Observatory

```{r observatory-overlay}
filtered_data <- motifs %>% 
  filter(`observatory` == TRUE)

jdp_map %>% 
  addCircleMarkers(
    data = filtered_data,
    color = "red"
  )
```


